Use-case: evaluation of network inference

### 2019-11-18 analysis/vignette_network_inference.Rmd
use knockout ground truths

      tibble(
        i,
        from,
        to,
        orig_prop,
        new_prop,
        reg_effect = orig_prop - new_prop,
        buffer_val = traj$feature_network_sc[1,paste0("regulation_", from, "_", to)]
      )
    }
  ))
max_prot <- model$feature_info %>% select(feature_id, max_protein) %>% deframe()
wpr <- model$feature_info %>% select(feature_id, wpr) %>% deframe()
xdr <- model$feature_info %>% select(feature_id, xdr) %>% deframe()
ggplot(knockouts) +
  geom_point(aes(log10(buffer_val), reg_effect / (wpr[to] - xdr[to]), colour = feature_network$effect %>% as.character)) +
  theme_bw()

feature_network$derivative <- 
  pbapply::pblapply(seq_len(nrow(feature_network)), function(i) {
  from <- feature_network$from[[i]]
  to <- feature_network$to[[i]]

  reaction <- reactions[[paste0("transcription_", to)]]
  prop <- gsub("pow\\(([^,]*) *, *([^\\)]*)\\)", "(\\1)^(\\2)", reaction$propensity)
  props <- prop %>% strsplit(" *; *") %>% first()
  propone <- props %>% last()
  subs <- tibble(
    var = gsub(" *=.*", "", props[-length(props)]),
    val = gsub(".*= *", "", props[-length(props)])
  )
  for (j in seq_len(nrow(subs))) {
    propone <- gsub(subs$var[[j]], subs$val[[j]], propone, fixed = TRUE)
  }

  deriv <- D(parse(text = propone), paste0("y_", from))
})

state <- c(
  model$simulations$counts[traj$cell_info$step_ix[[1]],],
  model$simulation_system$parameters
)
deriv <- feature_network$derivative[[1]]
# list2env(as.list(state), .GlobalEnv)
# eval(deriv)
env <- new.env()
list2env(as.list(state), env)

derivs <- map_dbl(feature_network$derivative, ~ eval(., envir = env))
reac_props <- model$simulations$reaction_propensities[traj$cell_info$step_ix[[1]], paste0("transcription_", model$feature_network$to)]

qplot(
  log10(traj$feature_network_sc[1,]),
  derivs,
  colour = reac_props
  # colour = as.character(feature_network$effect)
) + labs(
  x = "log10 sc importance = log10((y/k)^c)",
  y = "deriv. propensity function", 
  colour = "effect"
) +
  theme_bw() +
  viridis::scale_colour_viridis()
ggsave("~/deriv.pdf", width = 10, height = 10)

qplot(
  log10(traj$feature_network_sc[1,]),
  knockouts$reg_effect,
  colour = as.character(feature_network$effect)
) + labs(
  x = "log10 sc importance = log10((y/k)^c)",
  y = "KO", 
  colour = "effect"
) +
  theme_bw()

qplot(
  reac_props,
  derivs
) +
  theme_bw()

qplot(
  reac_props,
  log10(traj$feature_network_sc[1,])
) +
  theme_bw()
```

>>>>

      tibble(
        i,
        from,
        to,
        orig_prop,
        new_prop,
        reg_effect = orig_prop - new_prop,
        buffer_val = traj$feature_network_sc[1,paste0("regulation_", from, "_", to)]
      )
    }
  ))
fito <- model$feature_info %>% slice(match(knockouts$to, feature_id)) %>% 
  mutate(label = ifelse(is.na(module_id), gsub("[0-9]*$", "", feature_id), gsub("[0-9]*$", "", module_id)))
ggplot(knockouts) +
  geom_point(aes(log10(buffer_val), reg_effect / fito$wpr, colour = fito$label)) +
  theme_bw()

ggplot(knockouts) +
  geom_point(aes((buffer_val), reg_effect / fito$wpr, colour = factor(fito$basal))) +
  theme_bw() +
  scale_x_log10()
```
